TODO: Title

### 2013-02-26 Doc/Miccai2013/miccai2013.tex
abstract v1.0
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@516 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

% TODO
\begin{abstract}
TODO: Abstract
\keywords{liver, Glisson's capsule, deformation modeling, membrane}
\end{abstract}

>>>>

% TODO
\begin{abstract}
This work provides a complete physical model for the deformations of the liver with its three constituents: parenchyma, vessels and the Glisson's capsule.
Some recent experimental results \cite{Ahn2010} have shown that there is a significant difference of stiffness between the Glisson's capsule and the parenchyma. 
Moreover, it has been observed that the capsule plays an important role for the deformation at the local level \cite{Hollenstein2006}.
However, the Glisson's capsule is very thin and its influence for the global deformations of the liver was never highlighted.
In this work, we propose to use a membrane FEM model for the capsule, that is coupled with a vascularized model of the liver.
We show that the approach is able to reproduce the deformations observed at the local level.
Additionally, we show, by simulating natural global deformations of the liver observed on real images (due to gravity), that the results have important differences with and without the capsule.

\keywords{liver, Glisson's capsule, deformation modeling, membrane}
\end{abstract}
